The Chemistry Development Kit (CDK). 3. Atom typing, Rendering, Molecular Formula, and Substructure Searching

### 2013-10-06 article.tex
Revert to BibTeX

% Load packages
\usepackage{url}  % Formatting web addresses  
\usepackage{ifthen}  % Conditional 
\usepackage{multicol}   %Columns
\usepackage[utf8]{inputenc} %unicode support
%\usepackage[applemac]{inputenc} %applemac support if unicode package fails
%\usepackage[latin1]{inputenc} %UNIX support if unicode package fails
\urlstyle{rm}
\usepackage[citestyle=numeric-comp]{biblatex}                                                                     
\setlength{\bibitemsep}{0cm}                                                                                                                
\renewbibmacro{in:}{%                                                                                                                       
  \ifentrytype{article}{}{%                                                                                                                 
  \printtext{\bibstring{in}\intitlepunct}}}                                                                                                 
\addbibresource{bmc_article.bib}

@@

Recent prominent use cases of the CDK~\cite{Steinbeck2003,Steinbeck2006} \ldots (EGON)
AMBIT, ScaffoldHunter, OMG, ...

>>>>

% Load packages
\usepackage{url}  % Formatting web addresses  
\usepackage{ifthen}  % Conditional 
\usepackage{multicol}   %Columns
\usepackage[utf8]{inputenc} %unicode support
%\usepackage[applemac]{inputenc} %applemac support if unicode package fails
%\usepackage[latin1]{inputenc} %UNIX support if unicode package fails
\urlstyle{rm}
\usepackage{cite}

@@

Recent prominent use cases of the CDK~\cite{Steinbeck2003,Steinbeck2006} \ldots (EGON)
AMBIT~\cite{jeliazkova2011ambit}, jCompoundMapper~\cite{Hinselmann2011},
ScaffoldHunter~\cite{wetzel2009interactive}, OMG~\cite{Peironcely2012}, Padel~\cite{yap2011padel}, ...

Plugins for Taverna\cite{Truszkowski2011}, KNIME\cite{Beisken2013}, ...

Some extensions make it back into the main library, like SMSD~\cite{} and fingerprints from Padel.
Not all extensions made it back into the main library, such as those from
AMBIT-SMARTS~\cite{jeliazkova2011ambitsmarts}, AMBIT-Tautomer~\cite{kochev2013ambit}, FooFromRydberg~\cite{}.
